Topological Equivariant Artist Model for Visualization Library Architecture

### 2021-12-01 paper/main.tex
E restricted to U in presheaf equation

\begin{equation}
  \label{eq:related-work:continuity:presheaf}
  \begin{tikzcd}[column sep=small]
    {\cgamma{\opensetc_1}{\dtotalc}} & {} & {\cgamma{\opensetc_2}{\dtotalc}} \arrow[ll, "\iota^*"', hook'] \\& &\\
    \opensetc_1 \arrow[uu, "\sheafc_{\dtotal}"] \arrow[rr, "\iota"', hook] & {} \arrow[uu, "\sheafc_{\dtotal}" description, dotted] & \opensetc_2 \arrow[uu, "\sheafc_\dtotal"']                    
    \end{tikzcd}
\end{equation}

>>>>

\begin{equation}
  \label{eq:related-work:continuity:presheaf}
  \begin{tikzcd}[column sep=small]
    {\cgamma{\opensetc_1}{\dtotalc|_{\opensetc_1}}} & {} & {\cgamma{\opensetc_2}{\dtotalc|_{\opensetc_2}}} \arrow[ll, "\iota^*"', hook'] \\& &\\
    \opensetc_1 \arrow[uu, "\sheafc_{\dtotal}"] \arrow[rr, "\iota"', hook] & {} \arrow[uu, "\sheafc_{\dtotal}" description, dotted] & \opensetc_2 \arrow[uu, "\sheafc_\dtotal"']                    
    \end{tikzcd}
\end{equation}
